---
title: "Exploratory Data Analysis Assignment"
author: "Khadija Y, Nardos T, Meas K"
date: "5/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}
library("Tidyverse")
library("dplyr")
library("stringr")
library("ggplot2")
source("Chart 1.R")
source("Chart 2.R")
source("Chart 3.R")
source("Aggregated data(Exploratory Data Analysis).R")
source("Summary Information-Exploratory Analysis.R")
```
##Introduction
We are interested in focusing on the impacts of Covid-19, specifically in relations to race and death.Its clear that throughout the pandemic, the impacts of COVID-19 have varied in race, death, vaccination rates among other categories. As students of healthcare field related majors (Public Health, Medical Anthropology) we were interested in seeing data on how COVID has affected populations by race and deaths.
#DataSet Information
My group had retrieved our dataset from the CDC and included the raw data into github so that it was more accessible for this assignment.This is the website that we originally found our dataset.https://data.cdc.gov/NCHS/Distribution-of-COVID-19-Deaths-and-Populations-by/jwta-jxbg/data

#Summary Information 
install.packages("dplyr")
library("dplyr")

Covid_Demo<- read.csv("https://raw.githubusercontent.com/narditek/Exploratory-Analysis-Impacts-of-COVID-in-relations-with-Race-and-Deaths/main/Distribution_of_COVID-19_Deaths_and_Populations__by_Jurisdiction__Age__and_Race_and_Hispanic_Origin%20(1).csv")

summary_info<-list()
summary_info$num_observations<- nrow(Covid_Demo)
- For this portion of the summary info, we found that there are 3,710 rows within this study.
summary_info$num_features<- ncol(Covid_Demo)
For this portion of the summary info, we found that there are 13 columns within this study.

summary_info$most_state_death<- max(Covid_Demo$State)
We used this to find out the state with the most state deaths and we found that Wyoming has the state with the highest deaths. 
summary_info$most_race_death<- max(Covid_Demo$Race.Hispanic.origin)
With this, we wanted to know the highest death number specifically for the hispanic race. 
summary_info$mean_covid_death<- mean(Covid_Demo$Count.of.COVID.19.deaths)
na.omit(summary_info$mean_covid_death)
With this information, we wanted to know the mean of covid deaths within this dataset.

summary_info$most_state_death<- Covid_Demo %>%
  filter(Count.of.COVID.19.deaths == max(Count.of.COVID.19.deaths, na.rm = T)) %>%
  select(Count.of.COVID.19.deaths, State)
This would list out the count of covid deaths as well as the states. 

#Aggregated Table 
#load the tidyverse, dplyr, stringr package
install.packages("tidyverse")
library(tidyverse)
install.packages("dplyr")
library("dplyr")
install.packages("stringr")
library(stringr)


#load the dataset
Covid_Dem<-read_csv("https://raw.githubusercontent.com/narditek/Exploratory-Analysis-Impacts-of-COVID-in-relations-with-Race-and-Deaths/main/Distribution_of_COVID-19_Deaths_and_Populations__by_Jurisdiction__Age__and_Race_and_Hispanic_Origin%20(1).csv")
#create a new dataset that includes only the following columns: Race/Hispanic origin, Count of Covid-19 Death, and state
Covid_Dem_dataset <- Covid_Dem[c("State", "Race/Hispanic origin" ,"Count of COVID-19 deaths")]
#total deaths by covid by States
state_death<-Covid_Dem_dataset %>% 
  group_by(State) %>% 
  summarize(Count=n()) %>% 
  arrange(Count)

#The States, specifically top 3 states with the highest Covid deaths
Covid_dem_State_3_highest_death<-State_death %>% 
  head(3)
## Including Charts
#Chart 1


You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(group_state_death)
```
# Load ggplot2
library(ggplot2)

Covid_Demo<- read.csv("https://raw.githubusercontent.com/narditek/Exploratory-Analysis-Impacts-of-COVID-in-relations-with-Race-and-Deaths/main/Distribution_of_COVID-19_Deaths_and_Populations__by_Jurisdiction__Age__and_Race_and_Hispanic_Origin%20(1).csv")

group_state_death<-group_by(Covid_Demo, Count.of.COVID.19.deaths, State)

ggplot(group_state_death,aes(x =Count.of.COVID.19.deaths, y= State)) +
  geom_bar(stat = "identity")
  
  We created a bar graph to see the correaltion between the covid deaths compared to the state levels.
#Chart 2
```{r pressure, echo=FALSE}
plot(Covid_Demo))
```
We created a box plot to see how the the correlation between death rates compared to certain races, in this case we used those of hispanic orgin.
library("ggplot2")
library(viridis)
library(hrbrthemes)

Covid_Demo<- read.csv("https://raw.githubusercontent.com/narditek/Exploratory-Analysis-Impacts-of-COVID-in-relations-with-Race-and-Deaths/main/Distribution_of_COVID-19_Deaths_and_Populations__by_Jurisdiction__Age__and_Race_and_Hispanic_Origin%20(1).csv")
Covid_Demo%>%
ggplot(aes(x=Count.of.COVID.19.deaths, y= Race.Hispanic.origin, fill= Count.of.COVID.19.deaths)) +
 geom_boxplot() +
 scale_fill_viridis(discrete = TRUE, alpha= 0.6, option = "A") +
 theme_ipsum () +
 theme (
   legend.position = "none",
   plot.title = element_text(size=11)
 ) +
   ggtitle("Basic boxplot") +
   xlab("")
 
 ```{r pressure, echo=FALSE}
plot(Covid_Dem))
```
#Chart 3
We used a histogram because we wanted to compare the distribution of covid 19 deaths to race, origin and state
#load the dataset and package
install.packages("tidyverse")
library(tidyverse)
install.packages("dplyr")
library("dplyr")
install.packages("stringr")
library(stringr)
library(ggplot2)


#load/create the dataset
Covid_Dem<-read.csv("https://raw.githubusercontent.com/narditek/Exploratory-Analysis-Impacts-of-COVID-in-relations-with-Race-and-Deaths/main/Distribution_of_COVID-19_Deaths_and_Populations__by_Jurisdiction__Age__and_Race_and_Hispanic_Origin%20(1).csv")

#Make the histogram
Covid_Dem %>%
  filter(Distribution.of.COVID.19.deaths....<500 ) %>%
  ggplot( aes(x=Distribution.of.COVID.19.deaths....)) +
  geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)
  


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
